Predator clusters

### 2023-02-22 reports/04_pred_clus.qmd
Clean up predator table in cluster report

Following the methods of Dietrich et al. (2021), clustering analysis is restricted to species sighted near 5% or more of stations. This avoids granting undue leverage to rare species. `r n_distinct(predators_abundant$species)` species retained (SNPT to MIWH).

@@

total_stations <- n_distinct(zoop_sf$amlr.station)
predators_stations %>%
  group_by(amlr.station, species) %>% 
  summarize(count = sum(count), .groups = "drop") %>%
  group_by(species) %>%
  summarize(stations_present = n(),
            station_frac = stations_present / total_stations,
            .groups = "drop") %>%
  arrange(desc(station_frac)) %>% 
  knitr::kable()

>>>>

Following the methods of Dietrich et al. (2021), clustering analysis is restricted to species sighted near 5% or more of stations. This avoids granting undue leverage to rare species. `r n_distinct(predators_abundant$species)` species retained (i.e., species above red line).

@@

total_stations <- n_distinct(zoop_sf$amlr.station)
pred_frac <- predators_stations %>%
  group_by(amlr.station, species) %>% 
  summarize(count = sum(count), .groups = "drop") %>%
  group_by(species) %>%
  summarize(stations_present = n(),
            station_frac = stations_present / total_stations,
            .groups = "drop") %>%
  arrange(desc(station_frac))
cutoff_row <- sum(pred_frac$station_frac >= 0.05)

frac_fn <- scales::label_percent(accuracy = 0.1)
pred_frac %>% 
  set_names(c("Species", "Stations", "Fraction")) %>% 
  mutate(Fraction = frac_fn(Fraction)) %>% 
  knitr::kable(align = "lrr") %>% 
  kableExtra::kable_styling("striped",
                            full_width = FALSE) %>% 
  kableExtra::row_spec(cutoff_row, 
                       extra_css = "border-bottom: 2px dashed red")
